\fontfamily{phv}\selectfont{Research A Proposal}

### 2013-09-24 docs/proposal/doc.tex
Added effective connectivity
Made a start to the motivation.

@@

% Motivation
%This is part of why it is interesting to investigate neuro-degenerative disease, which are able to cripple our usually robust networks effectively.
%We want to learn more about our brains, as well as the diseases that target them.

@@

\subsection*{Brain connectivity}
% Functional connectivity
%Functional connectivity is defined as the temporal dependence of neuronal activity patterns of anatomically separated brain regions \cite{friston1993functional}.
%An increasing body of studies successfully investigates functional connectivity by applying statistical methods on the level of co-activation of resting-state fMRI time-series between brain regions.
%Several studies have shown that resting-state networks reflect brain connectivity in a concise way, though their exact relation remains unknown \cite{Lowe2000, doria2010, Bullmore2009}.
%Resting state indicating that subjects are instructed to relax without thinking of something in particular, to stimulate spontaneous brain activity.

>>>>

% vergelijking met granger causality, en andere methodes?

@@

% Motivation
The brain and particularly the human brain have been studied for hundreds of years.
Today, the secrets of our brains still belong to the most sought-after secrets.
The techniques however have changed.
Today, advanced measurement methods exist that allow scientists to peek inside brains that give a coarse but broad overview without having to open a single skull.

Of particular interest are causal relations between brain regions and cognitive and bodily functions.
We have come a long way since the time of Phrenology, the pseudoscience based on the idea that cognitive ability and personality could be derived from measurements of the skull.
The question whether brain region X is somehow connected to brain region Y is still highly relevant; it is the main question of the present-day scientific field of brain connectivity.

Understanding brain structure implies understanding more about the brain as a whole.

Brain connectivity also finds applications in medicine.
Neuro-degenerative diseases such as Alzheimer's disease, Parkinson's disease, dementia, Amyotrophic lateral sclerosis (ALS) have all been shown to severely alter brain connectivity.
Better methods for analysing connectivity could lead to more insight in these diseases.

%This is part of why it is interesting to investigate neuro-degenerative disease, which are able to cripple our usually robust networks effectively.
%We want to learn more about our brains, as well as the diseases that target them.

@@

\subsection*{Brain connectivity}
%Functional connectivity
%Functional connectivity is defined as the temporal dependence of neuronal activity patterns of anatomically separated brain regions \cite{friston1993functional}.
%An increasing body of studies successfully investigates functional connectivity by applying statistical methods on the level of co-activation of resting-state fMRI time-series between brain regions.
%Several studies have shown that resting-state networks reflect brain connectivity in a concise way, though their exact relation remains unknown \cite{Lowe2000, doria2010, Bullmore2009}.
%Resting state indicating that subjects are instructed to relax without thinking of something in particular, to stimulate spontaneous brain activity.
